---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SpraseVectorsHW6

<!-- badges: start -->
<!-- badges: end -->

The goal of SpraseVectorsHW6 is to create a new object type called **sparse vector** that reduces memory usage for vector that have large amounts of 0 values. Along with a new object, the package also has a variety of functions to manipluate sparse vectors.

## Installation

You can install the development version of SpraseVectorsHW6 like so:

``` r
remotes::install_github("MadelineRBoss/SparseVectorHW6")
```

## Examples

Creating a Sparse Vector

```{r example}
library(SpraseVectorsHW6)

x <- new("sparse_numeric",
                 value = c(1, 2, 3, 1),
                 pos = c(1L, 2L, 3L, 5L),
                 length = 10L)
y <- new("sparse_numeric",
                 value = c(4, 6, 1, 2),
                 pos = c(1L, 3L, 5L, 7L),
                 length = 10L)
```

Plot two vectors to see where they overlap
```{r}
plot(x, y)
```

Add, Multiply, Subtract, and Cross Product Vectors
```{r}
sparse_add(x,y)
x + y
```
```{r}
sparse_mult(x,y)
x * y
```
```{r}
print(sparse_sub(x,y))
x - y
```
```{r}
print(sparse_crossprod(x,y))
```

Get the sum, mean, norm, and standardize vector
```{r}
sparse_sum(x)
```

```{r}
mean(x)
```

```{r}
norm(x)
```

```{r}
standardize(x)
```

